---
title: "HW 4"
author: "Madi Polley"
date: "10/26/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(TSA)
```

**3a**

```{r}
data("winnebago")

plot(winnebago, type="o", ylab = "Winnebago Monthly Sales", main="Time Series of Monthly Unit Sales of RVs from Winnebago")
```

**The series is increasing with more variation as time increases. It appears that it may be exponential, so a log transformation may be appropriate to get more stationary values.**

**3b**

```{r}
plot(log(winnebago), type = "o", ylab = "Log(Monthly Sales)", main = "Time Series of Log( Monthly Unit Sales of RVs from Winnebago)")
```

**There is still an increase in the series, but it appears more linear now with less variation.**

**3c**

```{r}
percent = na.omit((winnebago - zlag(winnebago)) / zlag(winnebago))
plot(x = diff(log(winnebago))[-1], y = percent[-1], ylab = "Percent Change", xlab = "Difference of Logs")

cor(diff(log(winnebago))[-1], percent[-1])
```

**The plot is almost a straight line. This means there is likely strong correlation. The correlation coefficient is 0.9646886. This means that there is likely seasonality in the model that we have not considered.**

**4a**

```{r}
data(gold)
plot(gold, type = "o", ylab = "Daily Gold Prices", main = "Time Series of Daily Prices of Gold for the 252 Trading Days in 2005")
```

**The first half of the series has a seemingly constant price with some variation. The second half has a positive trend, possibly exponential.**

**4b**

```{r}
plot(diff(log(gold)), type = "o", ylab = "Differences of Log(Prices)", main = "Time Series of Log( Daily Price of Gold for the 252 Trading Days in 2005)")
```

**The plot appears stationary, but the variability gets larger as time goes on.**

**4c**

```{r}
acf(diff(log(gold)), main = "Simple ACF for the Differences of the Logs")
```

**The graph looks similar to the ACF for white noise. This means the log of gold prices may be a random walk model.**

**4d**

```{r}
hist(diff(log(gold)))
```

**4e**

```{r}
qqnorm(diff(log(gold)))
qqline(diff(log(gold)))

shapiro.test(diff(log(gold)))
```

**The QQ plot isn't straight, which means that the distribution is not normal. The Shapito-Wilk test value of 0.015 also shows that it is not normal.**