---
title: "349 Homework 6"
author: "Madi Polley"
date: "11/9/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(TSA)
```

**3a**

```{r}
series = arima.sim(n=30, list(ar = 0.5))
model1 = arima(series, order = c(1,0,0))
plot(rstandard(model1), ylab="Standardized Residuals", type = "o")
abline(h=0)
```

**Yes it supports AR(1). There are no obvious patterns in the residuals.**

**3b**

```{r}
qqnorm(residuals(model1))
qqline(residuals(model1))
```

**The QQ plot curls at the tails which means that the model is not normal.**

**3c**

```{r}
acf(residuals(model1))
```

**None of the lags surpass the dotted line, therefore the AR(1) is supported.**

**3d**

```{r}
LB.test(model1, lag = 8)
```

**The p-value is not significant for the first 8 autocorrelations, so we won't reject the randomness of the errors.**

**4a**

```{r}
data(hare)
model2 = arima(sqrt(hare), order = c(3,0,0))
acf(rstandard(model2))
```

**None of the lags are significant.**

**4b**

```{r}
LB.test(model2, lag = 9)
```

**The p-value is not significant for the first 9 autocorrelations of the residuals, which means we won't reject the randomness of the errors.**

**4c**

```{r}
runs(rstandard(model2))
```

**The number of runs isn't surprising. The p-value is also not significant so we fail to reject the independence of the error terms.**

**4d**

```{r}
qqnorm(residuals(model2))
qqline(residuals(model2))
```

**Since the tails are pretty far from the line, this is not normal.**

**4e**

```{r}
shapiro.test(residuals(model2))
```

**Since the p-value is not significant, we fail to reject the normality of the errors.**